---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# cranscan

The goal of cranscan is to make it easy to search for relevant R packages to your interests, using an interface based on [papr](https://github.com/jtleek/papr).

The first step in this is retrieving the data from CRAN, and then appending a download count to it.

```{r}
library(cranscan)

scan_cran_tbl <- scan_cran("miss | imp*")

scan_cran_tbl

```

# Future work

- adding download counts: Currently only 950 calls via `cranlogs::cran_downloads()` are made possible in a single call, need to work out how to get up to 10K.

- shiny app: there will of course be a shiny app that allows for swiping through relevant R packages and then having some clever way of handling what you liked and didn't like.

- some sort of machine-learning-y way to show CRAN packages that you might be interested in, based on previous swipe patterns?

- cranberry juice: another option to just view what has recently been pushed to cranberries.

